# Annex

```{r loading the packages, echo = FALSE, message = FALSE}
source(here::here("scripts", "setup.R"))
data <- read.csv(here("data", "TMS_dataset_Vaud_20240314_FINAL.csv"), sep = ",")
```

## Raw questions descriptions {#sec-data-description}

### Raw questions description in German

Find below the raw description translated in German:

```{r raw questions in german, echo = FALSE}
questions_ger <- read.csv(here("data", "questions_ger_export_20240503.csv"), sep = ";")
questions_ger <- questions_ger %>%
  select(Code = Name, Description = Beschriftung, Type = Werte) %>%
  na.omit() %>%
  slice(1:54)

questions_ger %>%
  kable("html", escape = FALSE) %>%
  kable_styling(bootstrap_options = c("striped",
                                      "hover",
                                      "condensed",
                                      "responsive"))
```

### Raw questions description in English

Find below the raw description translated in English:

```{r raw questions in english, echo = FALSE}
questions_eng <- read.csv(here("data", "questions_eng_export_20240430.csv"), sep = ";")
questions_eng <- questions_eng %>%
  select(Code = Name, Description = Lettering, Type = Values) %>%
  na.omit() %>%
  slice(1:54)

questions_eng %>%
  kable("html", escape = FALSE) %>%
  kable_styling(bootstrap_options = c("striped",
                                      "hover",
                                      "condensed",
                                      "responsive"))
```

## Data summary {#sec-data-summary}

Find below the full technical description of the dataset:

```{r echo = FALSE}
print(dfSummary(data), method = "render")
```

## Distribution of visitors per continent  {#sec-data-distributioncontinent}

```{r Percentage per continent of visitors coming in the canton of vaud, echo = FALSE}
datatable(F05_01_PCT,
          rownames = FALSE,
          options = list(pageLength = 10,
                         class = "hover",
                         searchHighlight = TRUE)) %>%
  formatPercentage('Percentage', 2)
```

## Global Distribution of Visitors to the Canton of Vaud by Nationality {#sec-data-distributionnationality}

```{r Global Distribution of Visitors to the Canton of Vaud by Nationality, echo=FALSE}
datatable(F05_02_PCT,
          rownames = FALSE,
          options = list(pageLength = 10,
                         class = "hover",
                         searchHighlight = TRUE))
```

## Percentage per continent of visitors coming in the canton of Vaud  {#sec-data-city_percentage_continent}

```{r Percentage per continent of visitors coming in the canton of Vaud, echo = FALSE}
datatable(F05_01_PCT,
          rownames = FALSE,
          options = list(pageLength = 10,
                         class = "hover",
                         searchHighlight = TRUE)) %>%
  formatPercentage('Percentage', 2)
```

## {#sec-data-city_percentage_country}

```{r Per city, the percentage of each visitor country of origin, relative to the number of visitor of the city, echo=FALSE}
datatable(nationality_ratio_per_city,
          rownames = FALSE,
          options = list(pageLength = 10,
                         class = "hover",
                         searchHighlight = TRUE))
```

## Distribution domestic visitors {#sec-data-domestic_visitors}

```{r Distribution among swiss visitors (scaled ratio), echo=FALSE}
datatable(Inside_Switzerland_ratio,
          options = list(pageLength = 10,
                         class = "hover",
                         searchHighlight = TRUE,
  columnDefs = list(list(targets = 4, visible = FALSE))),rownames = FALSE) %>%
  formatPercentage('Percentage', 2) %>%
  formatPercentage('Ratio', 5) %>%
  formatPercentage('Scaled_Ratio', 2)
```

## Distribution of Arrivals per Nationality {#sec-data-arrivals}

```{r Distribution of Arrivals per Nationality, echo=FALSE}
datatable(Inside_Switzerland_ratio,
          options = list(pageLength = 10,
                         class = "hover",
                         searchHighlight = TRUE,
  columnDefs = list(list(targets = 4, visible = FALSE))),rownames = FALSE) %>%
  formatPercentage('Percentage', 2) %>%
  formatPercentage('Ratio', 5) %>%
  formatPercentage('Scaled_Ratio', 2)
```

