---
format:
  html:
    code-fold: true
    fig-align: center
---

```{r Loading the packages and importing the data, output = FALSE, echo = FALSE}
source(here::here("scripts", "setup.R"))
data <- read.csv(here("data", "district_map.csv"),
                 sep = ",")
```

# Exploratory Data Analysis

## Visitor Demographics

### Global Distribution of Visitors in the Canton of Vaud by Continent

The survey gathered around 2500 responses from 100 different nationalities. We decided to to start by looking at the overall nationality distribution of the visitors. The full statistics and additional informations can be found in the "Annex"  section.

The graph below shows the percentage of visitors per continent who have visited the canton of Vaud. More detailed information on the distribution per continent can be found in the [Annex -@sec-data-distributioncontinent].

```{r, warning=FALSE, out.height="100%", out.width="100%", fig.width=7}
### F05_01.ENG ###

# nb of occurrences by country and continents 
OccurencesCountry <- data %>% 
  group_by(data$F05_02_ENG) %>% 
  count(sort = TRUE)
OccurencesContinent <- data %>% 
  group_by(data$F05_01_ENG) %>% 
  count(sort = TRUE)

# Continent in percentages
F05_01_PCT <- data %>% 
  group_by(F05_01_ENG) %>%
  summarise(Count = n()) %>%
  mutate(Percentage = Count / sum(Count)) %>% 
  arrange(desc(Percentage)) %>%
  rename(Continent_of_origin = F05_01_ENG)

# plot numbers continent 
ggplot(F05_01_PCT,
       aes(x=reorder(Continent_of_origin, Percentage*100),
           y=Percentage*100,
           fill=Continent_of_origin)) +
  geom_bar(stat="identity") +
  coord_flip() +
  theme_minimal() +
  labs(x="Continents",
       y="Percentages",
       title="Distribution of Visitors per Continent in Percentage, in the whole canton") +
  theme(legend.title = element_blank(),
        legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 10),
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_text(aes(label=sprintf("%.2f%%", Percentage*100)),
            position=position_dodge(width=-0.5),
            vjust=-0.01,
            hjust=-0.1,
            size = 3) +
  ylim(0, 90)
```

As we can see, the majority of respondents came from Europe (around 78%), followed by Asia (around 8%), North and Central America (around 8%), South America (around 3%), Australia and Oceania (around 2%) and Africa (around 1%).

### Global Distribution of Visitors in the Canton of Vaud by Nationality

Then we decided to explore the distribution of the nationalities per continent. Here is a graph showing our results. For better visibility, we have grouped most of the countries in the variable "Other Countries" and added them on the graph with the remaining top 7 most represented countries in the list. You can find the table of the occurrences and percentages per nationality in the [Annex -@sec-data-distributionnationality].

```{r,fig.width=10, fig.height=10, echo=FALSE}
# Countries in percentages 
F05_02_PCT <- data %>% 
  group_by(F05_02_ENG) %>%
  summarise(Count = n()) %>%
  mutate(Percentage = paste0(round((Count / sum(Count) * 100),2),"%")) %>% 
  arrange(desc(Count)) %>%
  rename(Country_of_origin = F05_02_ENG)

### F05_02_ENG ###
# plot with continents 
F05_02_PCT <- data %>%
  group_by(F05_02_ENG, F05_01_ENG) %>%  # Group by both country and continent
  summarise(Count = n(), .groups = 'drop') %>%
  mutate(Percentage = round((Count / sum(Count) * 100),2)) %>%
  arrange(desc(Percentage)) 

# concatenate all countries except " 7 best " 
F05_02_PCT <- F05_02_PCT %>% add_row(F05_01_ENG = "Other Continents", F05_02_ENG = "Other Countries", Count = sum(F05_02_PCT$Count[7:104]), Percentage = sum(F05_02_PCT$Percentage[7:104]))

# get rid of the rest of the rows
F05_02_PCT <- F05_02_PCT[-(8:104),]

# plot
ggplot(F05_02_PCT, aes(x = reorder(`F05_02_ENG`, Percentage), y = Percentage, fill = `F05_01_ENG`)) + 
  geom_bar(stat = "identity") +
  coord_flip() +
  scale_fill_brewer(palette = "Set3", name = "Continent") +
  theme_minimal() +
  labs(title = "Distribution of Visitors by Country and Continent of Origin in Percentages",
       x = "Country of Origin",
       y = "Percentages") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9), 
        axis.text.y = element_text(angle = 45, hjust = 1, size = 9),
        plot.title = element_text(hjust = 0.5, size = 15),
        legend.position = "right") +
  geom_text(aes(label=sprintf("%.2f%%", Percentage)),
            position=position_stack(vjust=0.5))
```

Our results show that Switzerland is the country most represented among all visitors (around 31.5%). The canton of Vaud therefore has a large number of domestic visitors. We can also see that the countries most represented are European, such as France (around 14.5%), the United Kingdom (around 7.5%), Germany (around 5.5%), Belgium (around 3.5%) and finally Spain (around 3%). The only other nationality from another continent represented here is the United States of America (around 5.5%). Proximity, for example, could be one of the main factors explaining these results.

## City and District Visitor Distributions

**Per city, the percentage of each visitor's country of origin, relative to the number of visitor of the city**

Now in order to know more precisely about the destination of the visitors, we have decided to gather by city the percentage of country of origin.

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# Counting the number of tourists by city and nationality
tourists_by_nationality <- data %>%
  group_by(F105_Code, F05_02_ENG) %>%
  summarise(Count = n(), .groups = 'drop')

# Calculating the total number of tourists per city
total_tourists_per_city <- tourists_by_nationality %>%
  group_by(F105_Code) %>%
  summarise(TotalCount = sum(Count), .groups = 'drop') %>%
  arrange(desc(TotalCount)) 

#top 10 cities 
# top_10_cities <- total_tourists_per_city %>%
#   arrange(desc(TotalCount)) %>%
#   head(10)

# Joining the counts back to the detailed breakdown and calculating the ratio
# nationality_ratio_per_city <- tourists_by_nationality %>%
#   left_join(total_tourists_per_city, by = "F105_Code") %>%
#   mutate(Ratio = round((Count / TotalCount),3)) %>%
#   select(F105_Code, F05_02_ENG, Ratio) %>%
#   rename(City = F105_Code, Country_of_origin = F05_02_ENG)

# Joining the counts back to the detailed breakdown and calculating the ratio
nationality_ratio_per_city <- tourists_by_nationality %>%
  left_join(total_tourists_per_city, by = "F105_Code") %>%
  arrange(desc(TotalCount))

# Step 1: Identify the top 10 cities by TotalCount
top_10_cities <- nationality_ratio_per_city %>%
  distinct(F105_Code, TotalCount) %>%
  arrange(desc(TotalCount)) %>%
  slice_head(n = 10) %>%
  pull(F105_Code)

# Step 2: Split the data into top 10 cities and the remaining cities
top_cities_data <- nationality_ratio_per_city %>%
  filter(F105_Code %in% top_10_cities)

other_cities_data <- nationality_ratio_per_city %>%
  filter(!F105_Code %in% top_10_cities)

# Step 3: Aggregate the remaining cities into a single "other" observation
other_summary <- other_cities_data %>%
  group_by(F05_02_ENG) %>%
  summarise(
    F105_Code = "Other",
    Count = sum(Count),
    TotalCount = sum(TotalCount)
  )

# Step 4: Combine the top 10 cities with the "other" observation
final_data <- bind_rows(
  top_cities_data,
  other_summary
)

NB_TotalCount_Other <- final_data %>% add_row(F105_Code = "Other Continents", F05_02_ENG = "Other Countries", Count = sum(final_data$Count[300:346]), TotalCount = sum(final_data$TotalCount[300:346])) %>% 
  filter(F105_Code =="Other Continents")

# Assuming your data frame is named `final_data`
final_data <- final_data %>%
  mutate(TotalCount = if_else(F105_Code == "Other", 473, TotalCount)) 

# Step 2: Group by F105_Code and compute the ratio
final_data <- final_data %>%
  group_by(F105_Code) %>%
  mutate(Ratio = round(Count / TotalCount, 3)) %>%
  ungroup()
  
final_data <- final_data %>%
  group_by(F105_Code, F05_02_ENG) %>%
  arrange(desc(Ratio))

# Step 3: Sum the Ratio for a specific city (e.g., "Lausanne")
sum_ratio_lausanne <- final_data %>%
  filter(F105_Code == "Morges") %>%
  summarise(SumRatio = sum(Ratio)) %>%
  pull(SumRatio) ###why > 1 ??


# Plotly
plot <- plot_ly(final_data, 
                x = ~F105_Code, 
                y = ~Ratio, 
                color = ~F05_02_ENG, 
                type = 'bar') %>%
  layout(title = 'Stacked Bar Plot of Ratios by City and Nationality',
         xaxis = list(title = 'City', tickangle = -45),
         yaxis = list(title = 'Ratio'),
         barmode = 'stack',
         showlegend = FALSE)  # Remove the legend

plot


# Create the stacked bar plot
# ggplot(final_data, aes(x = F105_Code, y = Ratio, fill = F05_02_ENG)) +
#   geom_bar(stat = "identity") +
#   labs(title = "Stacked Bar Plot of Ratios by City and Nationality",
#        x = "City",
#        y = "Ratio",
#        fill = "Nationality") +
#   theme_minimal() +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1),
#         legend.position = "none")

```

The percentage here was in fact a ratio representing the number of people from one particular nationality over the total number of visitors in each city. Unfortunately, as very few data has been collected in some cities, the ratio of visitor from one nationality over all the visitor surveyed can be really large (up to 1, in point of percentage). On the other hand, as data from some other city gathered a lot of answers, we observe that some country of origin (e.g. Austria in Lausanne) were only accounting for 0.2% of the total visitors.

**Ratio of each country of origin relatively to the number of tourist surveyed in each district**

In the same process, let's now explore the country of origin ratio per district of tourism.

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# ratio of each nationality relatively to the number of tourist surveyed in each district F105_OrgCode
tourists_by_nationality <- data %>%
  group_by(leaflet_districts, F05_02_ENG) %>%
  summarise(Count = n(), .groups = 'drop')

# Calculating the total number of tourists per city
total_tourists_per_city <- tourists_by_nationality %>%
  group_by(leaflet_districts) %>%
  summarise(TotalCount = sum(Count), .groups = 'drop')

# Joining the counts back to the detailed breakdown and calculating the ratio
nationality_ratio_per_city <- tourists_by_nationality %>%
  left_join(total_tourists_per_city, by = "leaflet_districts") %>%
  mutate(Ratio = round((Count / TotalCount),3)) %>%
  select(leaflet_districts, F05_02_ENG, Ratio) %>%
  rename(District_tourism = leaflet_districts,Country_of_origin = F05_02_ENG)

datatable(nationality_ratio_per_city, options = list(pageLength = 10,
                                   class = "hover",
                                   searchHighlight = TRUE), rownames = FALSE)
```

Again, the low number of data available in our data don't allow us to get really satisfying results for every city surveyed.

### Domestic Tourism

#### Global Swiss Domestic Visitors

As mentioned above, more than 30% of the visitors surveyed were Swiss. We therefore decided to find out more about the percentage of domestic visitors in the canton of Vaud. Here is the distribution of visitors by canton of origin, scaled by taking into account the population size of the cantons. This ensure the comparison between the different cantons.

```{r Ratio of each canton of origin relatively to the number of tourist surveyed in Switzerland, fig.width=10, fig.height=6, warning=FALSE, echo=FALSE}

## Séparation cantons suisse-allemands

 # Swiss german column

 # unique(data[data$F05_02 == "Schweiz", ]$F05_03)

 # Seratation german cantons (subjective)
 swiss_german_cantons = c("Luzern", "Schwyz", "Bern", "Neuenburg", "Aargau",
                          "Zürich", "Basel-Stadt", "Basel-Landschaft", "Obwalden",
                          "Appenzell Innerrhoden", "Schaffhausen", "Thurgau",
                          "St. Gallen", "Solothurn", "Uri", "Zug", "Nidwalden",
                          "Appenzell Ausserrhoden")

 # Binary column for swiss germans
 data$swiss_german <- ifelse(data$F05_02 == "Schweiz" & data$F05_03 %in% swiss_german_cantons, 1, 0)
 
 # count ratio from each german canton over the data
 Inside_Switzerland <- data %>% 
  select(F05_02_ENG, F05_03, swiss_german) %>%
  filter(F05_02_ENG == "Switzerland") %>%
  group_by(F05_03) %>%
  summarise(Count = n()) %>%
  mutate(Percentage = Count/sum(Count)) %>%
  rename(Canton = F05_03)


# Merging the population data with the original data
population_data <-
  data.frame(Canton = c("Aargau", "Appenzell Ausserrhoden",
                        "Appenzell Innerrhoden", "Basel-Landschaft",
                        "Basel-Stadt", "Bern", "Freiburg", "Genf", "Graubünden",
                        "Jura", "Luzern", "Neuenburg", "Nidwalden", "Obwalden",
                        "Schaffhausen", "Schwyz", "Solothurn", "St. Gallen",
                        "Tessin", "Thurgau", "Uri", "Waadt", "Wallis", "Zug",
                        "Zürich"),
             Population = c("704000", "56200", "16200", "292000", "204000",
                            "1045000", "338000", "499000", "200000", "74400",
                            "433000", "176000", "44300", "38600", "84000",
                            "166000", "278000", "515000", "353000", "282000",
                            "37000", "817000", "350000", "130000", "1605000"))

# replacing "Appenzell Innerrhoden " by "Appenzell Innerrhoden"
Inside_Switzerland$Canton[3] <- "Appenzell Innerrhoden"

# Merge the population data with your original data
data_merged <- merge(Inside_Switzerland, population_data,
                   by.x = "Canton",
                   by.y = "Canton",
                   all.x = TRUE)
data_merged$Population <- as.numeric(data_merged$Population)

# Calculating the ratio of occurrences per population for each canton
Inside_Switzerland_ratio <- data_merged %>%
  mutate(Percentage = Count/sum(Count)) %>%
  mutate(Ratio = Count / Population) %>%
  mutate(Scaled_Ratio = Ratio / sum(Ratio)) %>%
  select(Canton, Count, Percentage, Population, Ratio, Scaled_Ratio)

# # Now output the table with your custom settings
# datatable(Inside_Switzerland_ratio,
#           options = list(pageLength = 10,
#                          class = "hover",
#                          searchHighlight = TRUE,
#   columnDefs = list(list(targets = 4, visible = FALSE))),rownames = FALSE) %>%
#   formatPercentage('Percentage', 2) %>%
#   formatPercentage('Ratio', 5) %>%
#   formatPercentage('Scaled_Ratio', 2)

# plot scaled_ratio per canton
ggplot(Inside_Switzerland_ratio,
       aes(x=reorder(Canton, Scaled_Ratio),
           y=Scaled_Ratio)) +
  geom_bar(stat="identity",
           width = 0.8) +
  labs(title="Scaled Distribution of Domestic Visitor Cantons",
       x="Cantons",
       y="Percentages") +
  theme(legend.title = element_blank(),
        legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15, face = "bold"),
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.text.y = element_text(size = 6)) +
  geom_text(aes(label=sprintf("%.2f%%", 100 * Scaled_Ratio)),
            position=position_dodge(width=-0.5),
            vjust=0.3,
            hjust=-0.1,
            size = 3) +
  coord_flip() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 2)) +
  theme_minimal()
```

As can be seen from this table, the cantons with the highest percentage of domestic visitors scaled by the total population of these cantons are Vaud (around 8.5%), Uri (around 7.3%) and Obwalden (around 5.8%).

For the sake of readability and visualization, we decided to group the cantons into three categories: Swiss-Germans, Vaud, and the remaining Italian and Romansh-speaking cantons () under 'Other'. Since Vaud had the highest percentage of domestic visitors in the previous graph, we decided to give it its own category. Here is the scaled distribution of the swiss population surveyed:

```{r, echo = FALSE, message = FALSE, warning = FALSE}
  # Assuming 'Inside_Switzerland' has a column 'Canton' and you have a vector 'swiss_german_cantons' listing Swiss German cantons

Inside_Switzerland <- Inside_Switzerland_ratio %>%
  mutate(Categories = ifelse(Canton %in% swiss_german_cantons, "Swiss germans",
                             ifelse(Canton %in% c("Waadt"),"Vaud","Other"))) #Freiburg Genf Graubünden Jura Tessin Wallis

# Calculate counts for Swiss German cantons and others
counts <- Inside_Switzerland %>%
  group_by(Categories) %>%
  summarize(SumRatio = 100* sum(Scaled_Ratio), .groups = 'drop') %>%
  mutate(Categories = fct_reorder(Categories, SumRatio, .desc = TRUE))

# # Calculate total counts
# total_counts <- Inside_Switzerland %>% 
#   summarize(total = n())
# 
# # Calculate counts for Swiss German cantons and others
# counts <- Inside_Switzerland %>%
#   group_by(Categories) %>%
#   summarize(count = n(), .groups = 'drop')
# 
# # Calculate percentages
# counts <- counts %>%
#   mutate(percentage = count / total_counts$total * 100) %>%
#   mutate(Categories = fct_reorder(Categories, percentage, .desc = TRUE))



# Plot
ggplot(counts,
       aes(x = Categories,
           y = SumRatio,
           fill = Categories)) +
  geom_bar(stat = "identity") +
  # scale_x_discrete(labels = c("Others", "Swiss germans")) +
  theme_minimal() +
  theme(legend.position = "none") + 
  geom_text(aes(label=sprintf("%.2f%%", SumRatio)),
            position=position_stack(vjust=0.5)) + 
  labs(title = "Distribution of Swiss-German, Vaud and Other Cantons",
       x = "Cantons",
       y = "Percentages") +
  ylim(0, 90)
```

When looking at the total number of domestic visitors to Switzerland, around 70% come from the German-speaking part (18 cantons), which is more than three time as many as the 6 cantons under "Others" (Fribourg, Geneva, Grisons, Jura, Ticino, Valais) and more than 8 times as many as visitors from the canton of Vaud. 

Scaled, the percentage for the Canton of Vaud reaches 8.5%. Without scaling, it would only be 4%, meaning that there are more people coming in the canton of Vaud in comparison with the canton population than the other cantons (without any scaling, "Other" cantons would reach 24% and Swiss-Germans ones 72%).

## Destinations and Accomodations

> Where did they stay? (For example: yes, they went to Montreux, but what type of accommodation, what price?

### Most popular destinations in the canton Vaud

```{r Initialization and district creation, output = FALSE, echo = FALSE}
# Importing the data and loading the necessary packages
source(here::here("scripts", "setup.R"))
data <- read.csv(here("data", "TMS_dataset_Vaud_20240314_FINAL.csv"), sep = ",")

# Assign cities to districts
# Lausanne
data$leaflet_districts[data$F105_Code == "Lausanne"] <- "Lausanne"

# Riviera-Pays-d'Enhaut
data$leaflet_districts[data$F105_Code %in% c("Montreux", "Vevey", "La Tour-de-Peilz", "Rougemont", "Château-d'Oex", "Veytaux", "Rossinière", "Corsier-sur-Vevey", "Saint-Légier-La-Chiésaz", "Blonay", "Chardonne", "Chernex")] <- "Riviera-Pays-d'Enhaut"

# Morges
data$leaflet_districts[data$F105_Code %in% c("Morges", "Yens", "Aubonne")] <- "Morges"

# Jura-Nord vaudois
data$leaflet_districts[data$F105_Code %in% c("Yverdon-les-Bains", "L'Abbaye", "Vallorbe", "Orbe", "Yvonand", "La Praz", "Le Chenit", "Bullet", "Montagny-près-Yverdon", "Saint Croix", "Le Rocheray", "Le Pont", "Le Sentier", "Le Brassus", "Les Rasses", "Les Charbonnieres")] <- "Jura-Nord vaudois"

# Aigle
data$leaflet_districts[data$F105_Code %in% c("Aigle", "Leysin", "Villeneuve (VD)", "Ormont-Dessus", "Bex", "Lavey-Morcles", "Gryon", "Ormont-Dessous", "Les Diablerets", "Villars-sur-Ollon")] <- "Aigle"

# Nyon
data$leaflet_districts[data$F105_Code %in% c("Nyon", "Prangins", "Chavannes-de-Bogis", "Coppet", "Rolle", "Commugny", "Duillier", "Gilly", "Founex")] <- "Nyon"

# Broye-Vully
data$leaflet_districts[data$F105_Code %in% c("Valbroye", "Lucens", "Avenches", "Payerne", "Cudrefin", "St. Aubin", "Estavayer-le-Lac")] <- "Broye-Vully"

# Ouest lausannois
data$leaflet_districts[data$F105_Code %in% c("Crissier", "Bussigny", "Ecublens (VD)", "Renens", "Saint-Sulpice (VD)")] <- "Ouest lausannois"

# Lavaux-Oron
data$leaflet_districts[data$F105_Code %in% c("Chexbres", "Bourg-en-Lavaux", "Cully")] <- "Lavaux-Oron"

# Gros-de-Vaud
data$leaflet_districts[data$F105_Code %in% c("Echallens")] <- "Gros-de-Vaud"
```

Let's now dive into the subject of the location of their stay. First, let's have a look at the most popular locations in the canton Vaud. Given the architecture of the study this gives us the city where most people answer the survey.

```{r Most Popular City destinations, echo = FALSE}
# Assuming 'data' is already loaded
resort_counts <- table(data$F105_Code)

# Convert to data frame and calculate proportions
resort_counts_df <- as.data.frame(resort_counts)
names(resort_counts_df) <- c("Var1", "Freq")
resort_counts_df$Proportion <- resort_counts_df$Freq / sum(resort_counts_df$Freq)

# Generate hover text for all cities
resort_counts_df$HoverText <- paste("City name: ", resort_counts_df$Var1,
                                    "<br>Number of people visiting this city: ",
                                    resort_counts_df$Freq,
                                    "/", sum(resort_counts_df$Freq),
                                    "<br>Proportion of people visiting this city: ",
                                    percent(resort_counts_df$Proportion, accuracy = 0.01))

# Define a threshold for the smallest cities to be grouped
threshold <- 0.02  # Cities below 2% of the total visits

# Calculate the sum for 'Other Cities'
other_cities_freq <- sum(resort_counts_df$Freq[resort_counts_df$Proportion < threshold])
other_cities_proportion <- sum(resort_counts_df$Proportion[resort_counts_df$Proportion < threshold])

# Create a data frame entry for 'Other Cities' with identical columns
other_cities_df <- data.frame(Var1 = "Other Cities", 
                              Freq = other_cities_freq, 
                              Proportion = other_cities_proportion)

# Generate hover text specifically for 'Other Cities'
other_cities_df$HoverText <- paste("City name: Other Cities",
                                   "<br>Number of people visiting these cities: ",
                                   other_cities_df$Freq,
                                   "/", sum(resort_counts_df$Freq),
                                   "<br>Proportion of people visiting these cities: ",
                                   percent(other_cities_proportion, accuracy = 0.01))

# Remove cities below the threshold
resort_counts_df <- resort_counts_df[resort_counts_df$Proportion >= threshold, ]

# Append 'Other Cities' row to the data frame
resort_counts_df <- rbind(resort_counts_df, other_cities_df)

# Adjust factor levels based on Proportion descending for the plot
resort_counts_df$Var1 <-
  factor(resort_counts_df$Var1,
         levels = resort_counts_df$Var1[order(-resort_counts_df$Proportion)])

# Plot as a bar plot using updated data frame
plot_ly(resort_counts_df,
        x = ~Var1,
        y = ~Proportion,
        type = 'bar',
        text = "",
        hoverinfo = 'text',
        hovertext = ~HoverText,
        textposition = 'auto') %>%
  config(modeBarButtonsToRemove = c('pan2d', 'select2d', 'lasso2d', 'zoomIn2d',
                                    'zoomOut2d', 'autoScale2d', 'resetScale2d',
                                    'hoverClosestCartesian', 
                                    'hoverCompareCartesian',
                                    'toggleSpikelines', 'zoom')) %>%
  layout(title = 'Most Popular Destinations (City)',
         xaxis = list(title = 'City',
                      showgrid = FALSE,
                      zeroline = FALSE,
                      tickangle = 45),
         yaxis = list(title = 'Proportion',
                      showgrid = TRUE,
                      zeroline = FALSE,
                      tickformat = ',.0%'),
         hovermode = 'x')
```

From this plot, we can see that the most pupular city in the canton of Vaud is Lausanne. Let's now have a look at the type of accommodation where the visitor stayed in the canton of Vaud. We took the liberty to remove the `r data %>% filter(F125_ENG == "#N/A") %>% summarise(Count = n())` observation where the type of accommodation was not specified. We can now concentrate more our attention on the district where the people stayed.

::: panel-tabset
#### Total

```{r Most Popular District destinations, echo = FALSE}
# Proportion
resort_counts <- as.data.frame(table(data$leaflet_districts))
resort_counts_df$Proportion <- (resort_counts_df$Freq / sum(resort_counts_df$Freq))

# Adjust factor levels based on Proportion descending
resort_counts_df$Var1 <- factor(resort_counts_df$Var1, levels = resort_counts_df$Var1[order(-resort_counts_df$Proportion)])

# Custom hover text
resort_counts_df$HoverText <- 
  paste("District name: ", resort_counts_df$Var1,
        "<br>Number of people visiting this district: ",
        resort_counts_df$Freq, "/", sum(resort_counts_df$Freq),
        "<br>Proportion of people visiting this district: ",
        scales::percent(resort_counts_df$Proportion))

# Plot as a bar plot
plot_ly(resort_counts_df,
        x = ~Var1,
        y = ~Proportion,
        type = 'bar',
        text = "",
        hoverinfo = 'text',
        hovertext = ~HoverText,
        textposition = 'auto') %>%
  config(modeBarButtonsToRemove = c('pan2d', 'select2d', 'lasso2d', 'zoomIn2d',
                                    'zoomOut2d', 'autoScale2d', 'resetScale2d',
                                    'hoverClosestCartesian', 
                                    'hoverCompareCartesian',
                                    'toggleSpikelines', 'zoom')) %>%
  layout(title = 'Most Popular Destinations (District)',
         xaxis = list(title = 'District',
                      showgrid = FALSE,
                      zeroline = FALSE),
         yaxis = list(title = 'Proportion',
                      showgrid = TRUE,
                      zeroline = FALSE,
                      tickformat = ',.0%'),
         hovermode = 'closest')
```

#### Switzerland

```{r Most Popular District destinations Switzerland, echo = FALSE}
# Proportion
swiss_data_destination <- subset(data, F05_02_ENG == "Switzerland")
resort_counts_df <- as.data.frame(table(swiss_data_destination$leaflet_districts))
resort_counts_df$Proportion <- (resort_counts_df$Freq / sum(resort_counts_df$Freq))

# Adjust factor levels based on Proportion descending
resort_counts_df$Var1 <- factor(resort_counts_df$Var1, levels = resort_counts_df$Var1[order(-resort_counts_df$Proportion)])

# Custom hover text
resort_counts_df$HoverText <- 
  paste("District name: ", resort_counts_df$Var1,
        "<br>Number of people visiting this district: ",
        resort_counts_df$Freq, "/", sum(resort_counts_df$Freq),
        "<br>Proportion of people visiting this district: ",
        scales::percent(resort_counts_df$Proportion))

# Plot as a bar plot
plot_ly(resort_counts_df,
        x = ~Var1,
        y = ~Proportion,
        type = 'bar',
        text = "",
        hoverinfo = 'text',
        hovertext = ~HoverText,
        textposition = 'auto') %>%
  config(modeBarButtonsToRemove = c('pan2d', 'select2d', 'lasso2d', 'zoomIn2d',
                                    'zoomOut2d', 'autoScale2d', 'resetScale2d',
                                    'hoverClosestCartesian', 
                                    'hoverCompareCartesian',
                                    'toggleSpikelines', 'zoom')) %>%
  layout(title = 'Most Popular Destinations (District)',
         xaxis = list(title = 'District',
                      showgrid = FALSE,
                      zeroline = FALSE),
         yaxis = list(title = 'Proportion',
                      showgrid = TRUE,
                      zeroline = FALSE,
                      tickformat = ',.0%'),
         hovermode = 'closest')
```

#### France

```{r Most Popular District destinations France, echo = FALSE}
# Proportion
french_data_destination <- subset(data, F05_02_ENG == "France")
resort_counts_df <- as.data.frame(table(french_data_destination$leaflet_districts))
resort_counts_df$Proportion <- (resort_counts_df$Freq / sum(resort_counts_df$Freq))

# Adjust factor levels based on Proportion descending
resort_counts_df$Var1 <- factor(resort_counts_df$Var1, levels = resort_counts_df$Var1[order(-resort_counts_df$Proportion)])

# Custom hover text
resort_counts_df$HoverText <- 
  paste("District name: ", resort_counts_df$Var1,
        "<br>Number of people visiting this district: ",
        resort_counts_df$Freq, "/", sum(resort_counts_df$Freq),
        "<br>Proportion of people visiting this district: ",
        scales::percent(resort_counts_df$Proportion))

# Plot as a bar plot
plot_ly(resort_counts_df,
        x = ~Var1,
        y = ~Proportion,
        type = 'bar',
        text = "",
        hoverinfo = 'text',
        hovertext = ~HoverText,
        textposition = 'auto') %>%
  config(modeBarButtonsToRemove = c('pan2d', 'select2d', 'lasso2d', 'zoomIn2d',
                                    'zoomOut2d', 'autoScale2d', 'resetScale2d',
                                    'hoverClosestCartesian', 
                                    'hoverCompareCartesian',
                                    'toggleSpikelines', 'zoom')) %>%
  layout(title = 'Most Popular Destinations (District)',
         xaxis = list(title = 'District',
                      showgrid = FALSE,
                      zeroline = FALSE),
         yaxis = list(title = 'Proportion',
                      showgrid = TRUE,
                      zeroline = FALSE,
                      tickformat = ',.0%'),
         hovermode = 'closest')
```

#### United Kingdom

```{r Most Popular District destinations UK, echo = FALSE}
# Proportion
uk_data_destination <- subset(data, F05_02_ENG == "United Kingdom")
resort_counts_df <- as.data.frame(table(uk_data_destination$leaflet_districts))
resort_counts_df$Proportion <- (resort_counts_df$Freq / sum(resort_counts_df$Freq))

# Adjust factor levels based on Proportion descending
resort_counts_df$Var1 <- factor(resort_counts_df$Var1, levels = resort_counts_df$Var1[order(-resort_counts_df$Proportion)])

# Custom hover text
resort_counts_df$HoverText <- 
  paste("District name: ", resort_counts_df$Var1,
        "<br>Number of people visiting this district: ",
        resort_counts_df$Freq, "/", sum(resort_counts_df$Freq),
        "<br>Proportion of people visiting this district: ",
        scales::percent(resort_counts_df$Proportion))

# Plot as a bar plot
plot_ly(resort_counts_df,
        x = ~Var1,
        y = ~Proportion,
        type = 'bar',
        text = "",
        hoverinfo = 'text',
        hovertext = ~HoverText,
        textposition = 'auto') %>%
  config(modeBarButtonsToRemove = c('pan2d', 'select2d', 'lasso2d', 'zoomIn2d',
                                    'zoomOut2d', 'autoScale2d', 'resetScale2d',
                                    'hoverClosestCartesian', 
                                    'hoverCompareCartesian',
                                    'toggleSpikelines', 'zoom')) %>%
  layout(title = 'Most Popular Destinations (District)',
         xaxis = list(title = 'District',
                      showgrid = FALSE,
                      zeroline = FALSE),
         yaxis = list(title = 'Proportion',
                      showgrid = TRUE,
                      zeroline = FALSE,
                      tickformat = ',.0%'),
         hovermode = 'closest')
```

#### Germany

```{r Most Popular District destinations Germany, echo = FALSE}
# Proportion
germany_data_destination <- subset(data, F05_02_ENG == "Germany")
resort_counts_df <- as.data.frame(table(germany_data_destination$leaflet_districts))
resort_counts_df$Proportion <- (resort_counts_df$Freq / sum(resort_counts_df$Freq))

# Adjust factor levels based on Proportion descending
resort_counts_df$Var1 <- factor(resort_counts_df$Var1, levels = resort_counts_df$Var1[order(-resort_counts_df$Proportion)])

# Custom hover text
resort_counts_df$HoverText <- 
  paste("District name: ", resort_counts_df$Var1,
        "<br>Number of people visiting this district: ",
        resort_counts_df$Freq, "/", sum(resort_counts_df$Freq),
        "<br>Proportion of people visiting this district: ",
        scales::percent(resort_counts_df$Proportion))

# Plot as a bar plot
plot_ly(resort_counts_df,
        x = ~Var1,
        y = ~Proportion,
        type = 'bar',
        text = "",
        hoverinfo = 'text',
        hovertext = ~HoverText,
        textposition = 'auto') %>%
  config(modeBarButtonsToRemove = c('pan2d', 'select2d', 'lasso2d', 'zoomIn2d',
                                    'zoomOut2d', 'autoScale2d', 'resetScale2d',
                                    'hoverClosestCartesian', 
                                    'hoverCompareCartesian',
                                    'toggleSpikelines', 'zoom')) %>%
  layout(title = 'Most Popular Destinations (District)',
         xaxis = list(title = 'District',
                      showgrid = FALSE,
                      zeroline = FALSE),
         yaxis = list(title = 'Proportion',
                      showgrid = TRUE,
                      zeroline = FALSE,
                      tickformat = ',.0%'),
         hovermode = 'closest')
```

#### United States of America

```{r Most Popular District destinations USA, echo = FALSE}
# Proportion
usa_data_destination <- subset(data, F05_02_ENG == "United States of America")
resort_counts_df <- as.data.frame(table(usa_data_destination$leaflet_districts))
resort_counts_df$Proportion <- (resort_counts_df$Freq / sum(resort_counts_df$Freq))

# Adjust factor levels based on Proportion descending
resort_counts_df$Var1 <- factor(resort_counts_df$Var1, levels = resort_counts_df$Var1[order(-resort_counts_df$Proportion)])

# Custom hover text
resort_counts_df$HoverText <- 
  paste("District name: ", resort_counts_df$Var1,
        "<br>Number of people visiting this district: ",
        resort_counts_df$Freq, "/", sum(resort_counts_df$Freq),
        "<br>Proportion of people visiting this district: ",
        scales::percent(resort_counts_df$Proportion))

# Plot as a bar plot
plot_ly(resort_counts_df,
        x = ~Var1,
        y = ~Proportion,
        type = 'bar',
        text = "",
        hoverinfo = 'text',
        hovertext = ~HoverText,
        textposition = 'auto') %>%
  config(modeBarButtonsToRemove = c('pan2d', 'select2d', 'lasso2d', 'zoomIn2d',
                                    'zoomOut2d', 'autoScale2d', 'resetScale2d',
                                    'hoverClosestCartesian', 
                                    'hoverCompareCartesian',
                                    'toggleSpikelines', 'zoom')) %>%
  layout(title = 'Most Popular Destinations (District)',
         xaxis = list(title = 'District',
                      showgrid = FALSE,
                      zeroline = FALSE),
         yaxis = list(title = 'Proportion',
                      showgrid = TRUE,
                      zeroline = FALSE,
                      tickformat = ',.0%'),
         hovermode = 'closest')
```

#### Belgium

```{r Most Popular District destinations Belgium, echo = FALSE}
# Proportion
belgium_data_destination <- subset(data, F05_02_ENG == "Belgium")
resort_counts_df <- as.data.frame(table(belgium_data_destination$leaflet_districts))
resort_counts_df$Proportion <- (resort_counts_df$Freq / sum(resort_counts_df$Freq))

# Adjust factor levels based on Proportion descending
resort_counts_df$Var1 <- factor(resort_counts_df$Var1, levels = resort_counts_df$Var1[order(-resort_counts_df$Proportion)])

# Custom hover text
resort_counts_df$HoverText <- 
  paste("District name: ", resort_counts_df$Var1,
        "<br>Number of people visiting this district: ",
        resort_counts_df$Freq, "/", sum(resort_counts_df$Freq),
        "<br>Proportion of people visiting this district: ",
        scales::percent(resort_counts_df$Proportion))

# Plot as a bar plot
plot_ly(resort_counts_df,
        x = ~Var1,
        y = ~Proportion,
        type = 'bar',
        text = "",
        hoverinfo = 'text',
        hovertext = ~HoverText,
        textposition = 'auto') %>%
  config(modeBarButtonsToRemove = c('pan2d', 'select2d', 'lasso2d', 'zoomIn2d',
                                    'zoomOut2d', 'autoScale2d', 'resetScale2d',
                                    'hoverClosestCartesian', 
                                    'hoverCompareCartesian',
                                    'toggleSpikelines', 'zoom')) %>%
  layout(title = 'Most Popular Destinations (District)',
         xaxis = list(title = 'District',
                      showgrid = FALSE,
                      zeroline = FALSE),
         yaxis = list(title = 'Proportion',
                      showgrid = TRUE,
                      zeroline = FALSE,
                      tickformat = ',.0%'),
         hovermode = 'closest')
```

#### Spain

```{r Most Popular District destinations Spain, echo = FALSE}
# Proportion
spain_data_destination <- subset(data, F05_02_ENG == "Spain")
resort_counts_df <- as.data.frame(table(spain_data_destination$leaflet_districts))
resort_counts_df$Proportion <- (resort_counts_df$Freq / sum(resort_counts_df$Freq))

# Adjust factor levels based on Proportion descending
resort_counts_df$Var1 <- factor(resort_counts_df$Var1, levels = resort_counts_df$Var1[order(-resort_counts_df$Proportion)])

# Custom hover text
resort_counts_df$HoverText <- 
  paste("District name: ", resort_counts_df$Var1,
        "<br>Number of people visiting this district: ",
        resort_counts_df$Freq, "/", sum(resort_counts_df$Freq),
        "<br>Proportion of people visiting this district: ",
        scales::percent(resort_counts_df$Proportion))

# Plot as a bar plot
plot_ly(resort_counts_df,
        x = ~Var1,
        y = ~Proportion,
        type = 'bar',
        text = "",
        hoverinfo = 'text',
        hovertext = ~HoverText,
        textposition = 'auto') %>%
  config(modeBarButtonsToRemove = c('pan2d', 'select2d', 'lasso2d', 'zoomIn2d',
                                    'zoomOut2d', 'autoScale2d', 'resetScale2d',
                                    'hoverClosestCartesian', 
                                    'hoverCompareCartesian',
                                    'toggleSpikelines', 'zoom')) %>%
  layout(title = 'Most Popular Destinations (District)',
         xaxis = list(title = 'District',
                      showgrid = FALSE,
                      zeroline = FALSE),
         yaxis = list(title = 'Proportion',
                      showgrid = TRUE,
                      zeroline = FALSE,
                      tickformat = ',.0%'),
         hovermode = 'closest')
```
:::

As we can see, out of the `r n_distinct(data$F105_Code)` city surveyed in the `r n_distinct(data$leaflet_districts)` district, the most popular district is `r resort_counts_df$Var1[order(-resort_counts_df$Proportion)][1]`. This is not really suprising because of the way the data was collected. More people were surveyed in these city/districts than other smaller one. It is still interesting to have a look to keep this in mind.

### Type of Accommodation by country

Let's dive deeper into the most popular type of accomodation per country. You can find below a plot showing the proportion of each type of accomodation for all the contries and for the most represented countries in our data, Switzerland, France, UK, Germany, USA, Belgium and Spain.

::: panel-tabset
#### Total

```{r Type of accomodation, echo = FALSE}
data_accomodation <- subset(data, F125_ENG != "#N/A")

# Calculating the proportion of each accommodation type and ordering by those proportions
accommodation_proportion <- data_accomodation %>%
  group_by(F125_ENG) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  mutate(Proportion = Count / sum(Count)) %>%
  arrange(Proportion)

# Adjust the factor levels of F125_ENG to ensure the order in the plot
accommodation_proportion$F125_ENG <- factor(accommodation_proportion$F125_ENG, levels = accommodation_proportion$F125_ENG)

# Custom hover text
accommodation_proportion$HoverText <-
  paste("Accommodation type: ", accommodation_proportion$F125_ENG,
        "<br>Number of people staying in this type of accommodation: ",
        accommodation_proportion$Count,"/", sum(accommodation_proportion$Count),
        "<br>Proportion of people staying in this type of accommodation: ",
        percent(accommodation_proportion$Proportion, accuracy = 0.01))

# Creating the bar plot with ordered proportions
plot_ly(accommodation_proportion,
                y = ~F125_ENG,
                x = ~Proportion,
                type = 'bar',
                text = "",
                hoverinfo = 'text',
                hovertext = ~HoverText,
                textposition = 'auto',
                orientation = 'h') %>%
  config(modeBarButtonsToRemove = c('pan2d', 'select2d', 'lasso2d', 'zoomIn2d',
                                    'zoomOut2d', 'autoScale2d', 'resetScale2d',
                                    'hoverClosestCartesian', 
                                    'hoverCompareCartesian',
                                    'toggleSpikelines', 'zoom')) %>%
  layout(title = "Most Popular Accommodation Types",
         xaxis = list(title = "",
                      side = 'top',
                      tickformat = ",.0%"),
         yaxis = list(title = "Type of Accommodation",
                      automargin = TRUE))
```

#### Switzerland

```{r Type of accomodation swiss, echo = FALSE}
swiss_data_accomodation <- subset(data, F125_ENG != "#N/A" & F05_02_ENG == "Switzerland")

# Calculating the proportion of each accommodation type and ordering by those proportions
swiss_accommodation_proportion <- swiss_data_accomodation %>%
  group_by(F125_ENG) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  mutate(Proportion = Count / sum(Count)) %>%
  arrange(Proportion)

# Adjust the factor levels of F125_ENG to ensure the order in the plot
swiss_accommodation_proportion$F125_ENG <- factor(swiss_accommodation_proportion$F125_ENG, levels = swiss_accommodation_proportion$F125_ENG)

# Custom hover text
swiss_accommodation_proportion$HoverText <-
  paste("Accommodation type: ", swiss_accommodation_proportion$F125_ENG,
        "<br>Number of people staying in this type of accommodation: ",
        swiss_accommodation_proportion$Count,"/", sum(swiss_accommodation_proportion$Count),
        "<br>Proportion of people staying in this type of accommodation: ",
        percent(swiss_accommodation_proportion$Proportion, accuracy = 0.01))

# Creating the bar plot with ordered proportions
plot_ly(swiss_accommodation_proportion,
                y = ~F125_ENG,
                x = ~Proportion,
                type = 'bar',
                text = "",
                hoverinfo = 'text',
                hovertext = ~HoverText,
                textposition = 'auto',
                orientation = 'h') %>%
  config(modeBarButtonsToRemove = c('pan2d', 'select2d', 'lasso2d', 'zoomIn2d',
                                    'zoomOut2d', 'autoScale2d', 'resetScale2d',
                                    'hoverClosestCartesian', 
                                    'hoverCompareCartesian',
                                    'toggleSpikelines', 'zoom')) %>%
  layout(title = "Most Popular Accommodation Types for Swiss tourists",
         xaxis = list(title = "",
                      side = 'top',
                      tickformat = ",.0%"),
         yaxis = list(title = "Type of Accommodation",
                      automargin = TRUE))
```

#### France

```{r Type of accomodation french, echo = FALSE}
french_data_accomodation <- subset(data, F125_ENG != "#N/A" & F05_02_ENG == "France")

# Calculating the proportion of each accommodation type and ordering by those proportions
french_accommodation_proportion <- french_data_accomodation %>%
  group_by(F125_ENG) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  mutate(Proportion = Count / sum(Count)) %>%
  arrange(Proportion)

# Adjust the factor levels of F125_ENG to ensure the order in the plot
french_accommodation_proportion$F125_ENG <- factor(french_accommodation_proportion$F125_ENG, levels = french_accommodation_proportion$F125_ENG)

# Custom hover text
french_accommodation_proportion$HoverText <-
  paste("Accommodation type: ", french_accommodation_proportion$F125_ENG,
        "<br>Number of people staying in this type of accommodation: ",
        french_accommodation_proportion$Count,"/", sum(french_accommodation_proportion$Count),
        "<br>Proportion of people staying in this type of accommodation: ",
        percent(french_accommodation_proportion$Proportion, accuracy = 0.01))

# Creating the bar plot with ordered proportions
plot_ly(french_accommodation_proportion,
                y = ~F125_ENG,
                x = ~Proportion,
                type = 'bar',
                text = "",
                hoverinfo = 'text',
                hovertext = ~HoverText,
                textposition = 'auto',
                orientation = 'h') %>%
  config(modeBarButtonsToRemove = c('pan2d', 'select2d', 'lasso2d', 'zoomIn2d',
                                    'zoomOut2d', 'autoScale2d', 'resetScale2d',
                                    'hoverClosestCartesian', 
                                    'hoverCompareCartesian',
                                    'toggleSpikelines', 'zoom')) %>%
  layout(title = "Most Popular Accommodation Types for French tourists",
         xaxis = list(title = "",
                      side = 'top',
                      tickformat = ",.0%"),
         yaxis = list(title = "Type of Accommodation",
                      automargin = TRUE))
```

#### United Kingdom

```{r Type of accomodation uk, echo = FALSE}
british_data_accomodation <- subset(data, F125_ENG != "#N/A" & F05_02_ENG == "United Kingdom")

# Calculating the proportion of each accommodation type and ordering by those proportions
british_accommodation_proportion <- british_data_accomodation %>%
  group_by(F125_ENG) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  mutate(Proportion = Count / sum(Count)) %>%
  arrange(Proportion)

# Adjust the factor levels of F125_ENG to ensure the order in the plot
british_accommodation_proportion$F125_ENG <- factor(british_accommodation_proportion$F125_ENG, levels = british_accommodation_proportion$F125_ENG)

# Custom hover text
british_accommodation_proportion$HoverText <-
  paste("Accommodation type: ", british_accommodation_proportion$F125_ENG,
        "<br>Number of people staying in this type of accommodation: ",
        british_accommodation_proportion$Count,"/", sum(british_accommodation_proportion$Count),
        "<br>Proportion of people staying in this type of accommodation: ",
        percent(british_accommodation_proportion$Proportion, accuracy = 0.01))

# Creating the bar plot with ordered proportions
plot_ly(british_accommodation_proportion,
                y = ~F125_ENG,
                x = ~Proportion,
                type = 'bar',
                text = "",
                hoverinfo = 'text',
                hovertext = ~HoverText,
                textposition = 'auto',
                orientation = 'h') %>%
  config(modeBarButtonsToRemove = c('pan2d', 'select2d', 'lasso2d', 'zoomIn2d',
                                    'zoomOut2d', 'autoScale2d', 'resetScale2d',
                                    'hoverClosestCartesian', 
                                    'hoverCompareCartesian',
                                    'toggleSpikelines', 'zoom')) %>%
  layout(title = "Most Popular Accommodation Types for British tourists",
         xaxis = list(title = "",
                      side = 'top',
                      tickformat = ",.0%"),
         yaxis = list(title = "Type of Accommodation",
                      automargin = TRUE))
```

#### Germany

```{r Type of accomodation germany, echo = FALSE}
german_data_accomodation <- subset(data, F125_ENG != "#N/A" & F05_02_ENG == "Germany")

# Calculating the proportion of each accommodation type and ordering by those proportions
german_accommodation_proportion <- german_data_accomodation %>%
  group_by(F125_ENG) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  mutate(Proportion = Count / sum(Count)) %>%
  arrange(Proportion)

# Adjust the factor levels of F125_ENG to ensure the order in the plot
german_accommodation_proportion$F125_ENG <- factor(german_accommodation_proportion$F125_ENG, levels = german_accommodation_proportion$F125_ENG)

# Custom hover text
german_accommodation_proportion$HoverText <-
  paste("Accommodation type: ", german_accommodation_proportion$F125_ENG,
        "<br>Number of people staying in this type of accommodation: ",
        german_accommodation_proportion$Count,"/", sum(german_accommodation_proportion$Count),
        "<br>Proportion of people staying in this type of accommodation: ",
        percent(german_accommodation_proportion$Proportion, accuracy = 0.01))

# Creating the bar plot with ordered proportions
plot_ly(german_accommodation_proportion,
                y = ~F125_ENG,
                x = ~Proportion,
                type = 'bar',
                text = "",
                hoverinfo = 'text',
                hovertext = ~HoverText,
                textposition = 'auto',
                orientation = 'h') %>%
  config(modeBarButtonsToRemove = c('pan2d', 'select2d', 'lasso2d', 'zoomIn2d',
                                    'zoomOut2d', 'autoScale2d', 'resetScale2d',
                                    'hoverClosestCartesian', 
                                    'hoverCompareCartesian',
                                    'toggleSpikelines', 'zoom')) %>%
  layout(title = "Most Popular Accommodation Types for German tourists",
         xaxis = list(title = "",
                      side = 'top',
                      tickformat = ",.0%"),
         yaxis = list(title = "Type of Accommodation",
                      automargin = TRUE))
```

#### United States of America

```{r Type of accomodation usa, echo = FALSE}
american_data_accomodation <- subset(data, F125_ENG != "#N/A" & F05_02_ENG == "United States of America")

# Calculating the proportion of each accommodation type and ordering by those proportions
american_accommodation_proportion <- american_data_accomodation %>%
  group_by(F125_ENG) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  mutate(Proportion = Count / sum(Count)) %>%
  arrange(Proportion)

# Adjust the factor levels of F125_ENG to ensure the order in the plot
american_accommodation_proportion$F125_ENG <- factor(american_accommodation_proportion$F125_ENG, levels = american_accommodation_proportion$F125_ENG)

# Custom hover text
american_accommodation_proportion$HoverText <-
  paste("Accommodation type: ", american_accommodation_proportion$F125_ENG,
        "<br>Number of people staying in this type of accommodation: ",
        american_accommodation_proportion$Count,"/", sum(american_accommodation_proportion$Count),
        "<br>Proportion of people staying in this type of accommodation: ",
        percent(american_accommodation_proportion$Proportion, accuracy = 0.01))

# Creating the bar plot with ordered proportions
plot_ly(american_accommodation_proportion,
                y = ~F125_ENG,
                x = ~Proportion,
                type = 'bar',
                text = "",
                hoverinfo = 'text',
                hovertext = ~HoverText,
                textposition = 'auto',
                orientation = 'h') %>%
  config(modeBarButtonsToRemove = c('pan2d', 'select2d', 'lasso2d', 'zoomIn2d',
                                    'zoomOut2d', 'autoScale2d', 'resetScale2d',
                                    'hoverClosestCartesian', 
                                    'hoverCompareCartesian',
                                    'toggleSpikelines', 'zoom')) %>%
  layout(title = "Most Popular Accommodation Types for American tourists",
         xaxis = list(title = "",
                      side = 'top',
                      tickformat = ",.0%"),
         yaxis = list(title = "Type of Accommodation",
                      automargin = TRUE))
```

#### Belgium

```{r Type of accomodation belgium, echo = FALSE}
belgian_data_accomodation <- subset(data, F125_ENG != "#N/A" & F05_02_ENG == "Belgium")

# Calculating the proportion of each accommodation type and ordering by those proportions
belgian_accommodation_proportion <- belgian_data_accomodation %>%
  group_by(F125_ENG) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  mutate(Proportion = Count / sum(Count)) %>%
  arrange(Proportion)

# Adjust the factor levels of F125_ENG to ensure the order in the plot
belgian_accommodation_proportion$F125_ENG <- factor(belgian_accommodation_proportion$F125_ENG, levels = belgian_accommodation_proportion$F125_ENG)

# Custom hover text
belgian_accommodation_proportion$HoverText <-
  paste("Accommodation type: ", belgian_accommodation_proportion$F125_ENG,
        "<br>Number of people staying in this type of accommodation: ",
        belgian_accommodation_proportion$Count,"/", sum(belgian_accommodation_proportion$Count),
        "<br>Proportion of people staying in this type of accommodation: ",
        percent(belgian_accommodation_proportion$Proportion, accuracy = 0.01))

# Creating the bar plot with ordered proportions
plot_ly(belgian_accommodation_proportion,
                y = ~F125_ENG,
                x = ~Proportion,
                type = 'bar',
                text = "",
                hoverinfo = 'text',
                hovertext = ~HoverText,
                textposition = 'auto',
                orientation = 'h') %>%
  config(modeBarButtonsToRemove = c('pan2d', 'select2d', 'lasso2d', 'zoomIn2d',
                                    'zoomOut2d', 'autoScale2d', 'resetScale2d',
                                    'hoverClosestCartesian', 
                                    'hoverCompareCartesian',
                                    'toggleSpikelines', 'zoom')) %>%
  layout(title = "Most Popular Accommodation Types for Belgian tourists",
         xaxis = list(title = "",
                      side = 'top',
                      tickformat = ",.0%"),
         yaxis = list(title = "Type of Accommodation",
                      automargin = TRUE))
```

#### Spain

```{r Type of accomodation spain, echo = FALSE}
spanish_data_accomodation <- subset(data, F125_ENG != "#N/A" & F05_02_ENG == "Spain")

# Calculating the proportion of each accommodation type and ordering by those proportions
spanish_accommodation_proportion <- spanish_data_accomodation %>%
  group_by(F125_ENG) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  mutate(Proportion = Count / sum(Count)) %>%
  arrange(Proportion)

# Adjust the factor levels of F125_ENG to ensure the order in the plot
spanish_accommodation_proportion$F125_ENG <- factor(spanish_accommodation_proportion$F125_ENG, levels = spanish_accommodation_proportion$F125_ENG)

# Custom hover text
spanish_accommodation_proportion$HoverText <-
  paste("Accommodation type: ", spanish_accommodation_proportion$F125_ENG,
        "<br>Number of people staying in this type of accommodation: ",
        spanish_accommodation_proportion$Count,"/", sum(spanish_accommodation_proportion$Count),
        "<br>Proportion of people staying in this type of accommodation: ",
        percent(spanish_accommodation_proportion$Proportion, accuracy = 0.01))

# Creating the bar plot with ordered proportions
plot_ly(spanish_accommodation_proportion,
                y = ~F125_ENG,
                x = ~Proportion,
                type = 'bar',
                text = "",
                hoverinfo = 'text',
                hovertext = ~HoverText,
                textposition = 'auto',
                orientation = 'h') %>%
  config(modeBarButtonsToRemove = c('pan2d', 'select2d', 'lasso2d', 'zoomIn2d',
                                    'zoomOut2d', 'autoScale2d', 'resetScale2d',
                                    'hoverClosestCartesian', 
                                    'hoverCompareCartesian',
                                    'toggleSpikelines', 'zoom')) %>%
  layout(title = "Most Popular Accommodation Types for Spanish tourists",
         xaxis = list(title = "",
                      side = 'top',
                      tickformat = ",.0%"),
         yaxis = list(title = "Type of Accommodation",
                      automargin = TRUE))
```
:::

The most popular accommodation type in the canton of Vaud, according to a survey of 2,440 respondents, is the Hotel/SPA House, selected by 777 individuals. Notably, 293 people chose to stay at campsites. For Swiss respondents specifically, campsites rise to the second most popular option, with nearly 30% opting for this type of accommodation, while the Hotel/Spa House remains the top choice. Interestingly, the free apartment/house is highly favored by visitors from France, the United Kingdom, Germany, and Belgium, ranking in their top two choices. Conversely, visitors from the United States tend to prefer hotels, rented apartments/houses, or other types of accommodations over free apartments. Additionally, campsites are notably less popular among American visitors. Below, a word cloud illustrates other favored types of accommodation.

```{r wordcloud, echo = FALSE, warning = FALSE}
# Running the wordcloud script
source(here("scripts", "word_cloud_for_eda.R"))
```

Among the `{r} sum(words)` respondents who did not choose traditional accommodations, the most popular alternative was staying with family, as indicated by `{r} words[1]` individuals. Staying with friends was the second most common choice, favored by `{r} words[2]` respondents, while staying at someone else's house ranked third with `{r} words[3]` mentions.

### Hotels Stars

Now, let's have a look at the hotel standing of the places where the people stayed. This will highlight the quality of the stay per district.

```{r Assign numeric value to the stars, echo = FALSE}
data <- data %>% 
  mutate(F130_num = case_when(
    F130 == "*****" ~ 5,
    F130 == "****" ~ 4,
    F130 == "***" ~ 3,
    F130 == "**" ~ 2,
    F130 == "*" ~ 1,
    TRUE ~ NA_real_))
```

#### Average Stars per District

```{r Average Stars per City, echo = FALSE, warning = FALSE}
# Calculation of the average of F130_num by F105_OrgCode, ordered by average
average_per_city <- data %>%
  group_by(leaflet_districts) %>%
  summarise(Average_F130_num = round(mean(F130_num, na.rm = TRUE), digits=2)) %>%
  arrange(desc(Average_F130_num))

# Create ordered cities list for plotly
ordered_cities <- average_per_city$leaflet_districts

# Calculate the number of observations per city (F105_OrgCode)
observations_per_district <- data %>%
  group_by(leaflet_districts) %>%
  summarise(Count = n())

# Join datasets to ensure alignment
combined_data <- left_join(average_per_city,
                           observations_per_district,
                           by = "leaflet_districts")

# Custom hover text
combined_data$HoverText <-
  paste("District name: ", combined_data$leaflet_districts,
        "<br>Average Stars: ", combined_data$Average_F130_num, "★",
        "<br>Number of people visiting this district: ", combined_data$Count,
        "/", sum(combined_data$Count))

# Creation of the plotly
plot_ly(combined_data,
        x = ~leaflet_districts,
        y = ~Average_F130_num,
        type = 'bar',
        text = "",
        hoverinfo = 'text',
        hovertext = ~HoverText,
        name = 'Average Stars') %>%
  config(modeBarButtonsToRemove = c('pan2d', 'select2d', 'lasso2d', 'zoomIn2d',
                                    'zoomOut2d', 'autoScale2d', 'resetScale2d',
                                    'hoverClosestCartesian', 
                                    'hoverCompareCartesian',
                                    'toggleSpikelines', 'zoom')) %>%
  layout(title = "Average Stars per District",
         xaxis = list(title = "District",
                      type = "category",
                      categoryorder = "array",
                      categoryarray = ordered_cities),
         yaxis = list(title = "Average Stars"),
         hovermode = "closest") 
```

As we can see on the graph above, the best average is optain in `r combined_data$leaflet_districts[1]` with an average of `r combined_data$Average_F130_num[1]` stars. But this statistics is not very representative to the reality. Only `r combined_data$Count[1]` people answered the survey in this district which is not enough to have a good idea of the quality of the hotels in this district. The second best region after `r combined_data$leaflet_districts[1]` is `r combined_data$leaflet_districts[2]` with an average of `r combined_data$Average_F130_num[2]` stars. This district got with `r combined_data$Count[2]` observation which is more representative. This high score for the Region of `r combined_data$leaflet_districts[2]` is not really surprising given the fact that this place is well know for its luxury hotels.

## Spendings

> Expenses and where they come from, when, where and for which sector?

### Percentage of people with package & without package

To begin with, we can notice that there are 2 types of traveler spendings: the ones who come in Switzerland with no package, meaning they spend on different categories that are not included in the packages, and the ones who come with a package, which usually already includes some different categories.

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# Calculate the number of non-NA entries for each type of spending
spending_counts <- data %>%
  summarize(
    Package = sum(!is.na(F82_Total)),
    WithoutPackage = sum(!is.na(F81_Total))
  ) %>%
  gather(key = "PackageType", value = "Count")

# Calculate percentages
total_records <- sum(spending_counts$Count)
spending_counts <- spending_counts %>%
  mutate(Percentage = (Count / total_records) * 100)

# Plot the percentages with the percentage shown on the bars
ggplot(spending_counts, aes(x = PackageType, y = Percentage, fill = PackageType)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = sprintf("%.1f%%", Percentage)),  # Format the labels to one decimal place
            position = position_stack(vjust = 0.5),  # Adjust text to be inside the bars
            color = "black") +
  labs(title = "Percentage of Observations With and Without Package",
       x = "Type of Spending",
       y = "Percentage (%)") +
  scale_fill_brewer(palette = "Pastel1") + # Aesthetically pleasing color palette
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

A majority of people travelling in Vaud come without a package. Despite only having around 8% of travelers without a package, it is of interest for us to see where they come from.

### Percentage of package by continent

To do so, we decided to see it as percentage per continent.

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# Prepare the data by adding a binary column for package and non-package tours
data <- data %>%
  mutate(
    With_Package = ifelse(!is.na(F82_Total), 1, 0),  # 1 if there's a package, 0 otherwise
    Without_Package = ifelse(!is.na(F81_Total), 1, 0)  # 1 if there's no package, 0 otherwise
  )

# Summarize data to count the number of package and non-package tours by continent
continent_summary <- data %>%
  group_by(F05_01_ENG) %>%
  summarize(
    Total_Tours = n(),  # Total number of tours
    Package_Tours = sum(With_Package, na.rm = TRUE),  # Total package tours
    Non_Package_Tours = sum(Without_Package, na.rm = TRUE)  # Total non-package tours
  ) %>%
  mutate(
    Package_Tour_Percentage = (Package_Tours / Total_Tours) * 100  # Calculate the percentage
  ) %>%
  arrange(desc(Package_Tour_Percentage))  # Arrange continents in descending order of package tour percentage

# Plot the percentage of package tours by continent in descending order
p <- ggplot(continent_summary, aes(x = reorder(F05_01_ENG, -Package_Tour_Percentage), y = Package_Tour_Percentage, fill = F05_01_ENG)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = sprintf("%.1f%%", Package_Tour_Percentage)),  # Adding percentage labels
            vjust = -0.5, color = "black", size = 3.5) +  # Adjust vjust to position labels above bars
  labs(title = "Percentage of Package Tours by Continent",
       x = "Continent",
       y = "Percentage of Package Tours (%)") +
  scale_fill_brewer(palette = "Set3") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none") 

# Display the plot
print(p)
```

As a result, it is interesting to see that the main spenders in packages are from Asia, Africa and South America. It would be interesting to target travelers from these continents to package deals rather than the rest of nationalities.

### Average Spending by Category

Now let's have a look at the average spending per category. The aim would be to see in which category most of the travelers spend their money on.

::: panel-tabset
#### Without Package

```{r, echo = FALSE, message = FALSE, warning = FALSE}
spending_data <- data.frame(
  Spending_Type = c("Overnight stay", "Transports", "Food & Drink", "Souvenirs", "Other shopping", "Other expenses"),
  Amount = c(mean(data$F81_01, na.rm = TRUE), 
             mean(data$F81_02, na.rm = TRUE),
             mean(data$F81_03, na.rm = TRUE),
             mean(data$F81_04, na.rm = TRUE),
             mean(data$F81_05, na.rm = TRUE),
             mean(data$F81_06, na.rm = TRUE))
)

ggplot(spending_data, aes(x = Spending_Type, y = Amount, fill = Spending_Type)) +
  geom_bar(stat = "identity", color = "black") +
  labs(title = "Average Spending by Category (no package tour)", x = "Category", y = "Average Amount") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotate x-axis labels for readability
```

We observe that most of the expenses from the people coming to Vaud is in their overnight stay, followed by their eating expenses and the transports and souvenirs.

#### With Package

```{r, echo = FALSE, message = FALSE, warning = FALSE}
spending_data_package <- data.frame(
  Spending_Type = c("Package", "Overnight stay", "Transports", "Food & Drink", "Souvenirs", "Other shopping", "Other expenses"),
  Amount = c(mean(data$F82_01[data$F82_01 <= 30000], na.rm = TRUE), # Ici on modifie pour inclure seulement les packages qui coûtent en dessous de 30'000 CHF. On assume que les packages qui coûtent au dessus de ce montant ne sont pas en CHF, et donc biaisent le sample.
             mean(data$F82_02, na.rm = TRUE),
             mean(data$F82_03, na.rm = TRUE),
             mean(data$F82_04, na.rm = TRUE),
             mean(data$F82_05, na.rm = TRUE),
             mean(data$F82_06, na.rm = TRUE),
             mean(data$F82_07, na.rm = TRUE))
)

ggplot(spending_data_package, aes(x = Spending_Type, y = Amount, fill = Spending_Type)) +
  geom_bar(stat = "identity", color = "black") +
  labs(title = "Average Spending by Category", x = "Category", y = "Average Amount") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

For the ones with the package, most is spent on the package, then the eating expenses and finally with the overnight stay. This is explained by the fact that packages usually include transportation and activities, which have a pretty high cost in Switzerland.
:::

With these plots, we can observe that there is a difference in spending for people who traveled with a package compared to the ones travelling without a spending package. Overall, the main expenses of people with a package is the package itself, meaning that some of the other variables are already included in the package. On the other hand, without the package, it is interesting to see that the main spending is on the overnight stay, then the food & drinks and finally the souvenirs.

### Spending by Country

Here, we will focus on our 7 main countries, putting the rest of the countries into "other countries". By doing so, we can observe which countries has the most expenses within our main nationalities.

::: panel-tabset
#### Total spending (without package)

```{r, echo = FALSE, message = FALSE, warning = FALSE}

# Create a vector of countries to group as "other countries"
countries_to_group <- c("Switzerland", "France", "United Kingdom", "Germany", "United States of America", "Belgium", "Spain")

# Aggregate total spending for F81_Total and include continents
total_spending_F81 <- data[data$F81_Total < 30000,] %>%
  group_by(F05_02_ENG, F05_01_ENG) %>%
  summarize(Total_Spending_F81 = sum(F81_Total, na.rm = TRUE)) %>%
  mutate(F05_02_ENG_grouped = if_else(F05_02_ENG %in% countries_to_group, F05_02_ENG, "Other Countries")) %>%
  group_by(F05_02_ENG_grouped, F05_01_ENG) %>%
  summarize(Total_Spending_F81 = sum(Total_Spending_F81)) %>%
  arrange(desc(Total_Spending_F81))

# Plot for F81_Total with continent colors
ggplot(total_spending_F81, aes(x = reorder(F05_02_ENG_grouped, -Total_Spending_F81), y = Total_Spending_F81, fill = F05_01_ENG)) +
  geom_bar(stat = "identity") +
  labs(title = "Total Spending by Country", x = "Country", y = "Total Spending") +
  scale_fill_brewer(palette = "Set3", name = "Continent") + # Color based on continent
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        legend.position = "bottom")  # Position the legend at the bottom


```

Swiss travelers spend the most in total, followed by French and American travelers.

#### Total spending (with package)

```{r, echo = FALSE, message = FALSE, warning = FALSE}

# Create a vector of countries to group as "other countries"
countries_to_group <- c("Switzerland", "France", "United Kingdom", "Germany", "United States of America", "Belgium", "Spain")

# Aggregate total spending for F82_Total and include continents
total_spending_F82 <- data[data$F82_Total < 30000,] %>%
  group_by(F05_02_ENG, F05_01_ENG) %>%
  summarize(Total_Spending_F82 = sum(F82_Total, na.rm = TRUE)) %>%
  mutate(F05_02_ENG_grouped = if_else(F05_02_ENG %in% countries_to_group, F05_02_ENG, "Other Countries")) %>%
  group_by(F05_02_ENG_grouped, F05_01_ENG) %>%
  summarize(Total_Spending_F82 = sum(Total_Spending_F82)) %>%
  arrange(desc(Total_Spending_F82))

# Plot for F82_Total with continent colors
ggplot(total_spending_F82, aes(x = reorder(F05_02_ENG_grouped, -Total_Spending_F82), y = Total_Spending_F82, fill = F05_01_ENG)) +
  geom_bar(stat = "identity") +
  labs(title = "Total Spending by Country", x = "Country", y = "Total Spending") +
  scale_fill_brewer(palette = "Set3", name = "Continent") + # Color based on continent
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        legend.position = "bottom")  # Position the legend at the bottom


```

Looking at the packages, and as we observed in the percentage of package by continent above, Europeans and North Americans aren't the ones spending most in total on packages. It is rather Asians who do so.

#### Average spending (without package)

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# Create a vector of countries to group as "other countries"
countries_to_group <- c("Switzerland", "France", "United Kingdom", "Germany", "United States of America", "Belgium", "Spain")

# Reshape data from wide to long format
data_long <- data[data$F81_Total < 30000,] %>%
  pivot_longer(
    cols = F81_01:F81_06,
    names_to = "Spending_Category",
    values_to = "Amount"
  )

# Calculate the average spending for each country and each category
average_spending <- data_long %>%
  mutate(F05_02_ENG_grouped = if_else(F05_02_ENG %in% countries_to_group, F05_02_ENG, "Other Countries")) %>%
  group_by(F05_02_ENG_grouped, F05_01_ENG) %>%
  summarize(Average_Spending = mean(Amount, na.rm = TRUE)) %>%
  ungroup() %>%
  arrange(desc(Average_Spending))

# Optional: Aggregate to country level without distinguishing by category
average_spending_by_country <- average_spending %>%
  group_by(F05_02_ENG_grouped, F05_01_ENG) %>%
  summarize(Average_Spending = mean(Average_Spending, na.rm = TRUE)) %>%
  arrange(desc(Average_Spending))

# Plot the average spending by country in descending order
ggplot(average_spending_by_country, aes(x = reorder(F05_02_ENG_grouped, -Average_Spending), y = Average_Spending, fill = F05_01_ENG)) +
  geom_bar(stat = "identity") +
  labs(title = "Average Spending by Country", x = "Country", y = "Average Spending") +
  scale_fill_brewer(palette = "Set3", name = "Continent") + # Color based on continent
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        legend.position = "bottom")  # Position the legend at the bottom


```

Looking at averages, North Americans spend the most on average when coming to Vaud, followed by Belgium and the United Kingdom.

#### Average spending (with package)

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# Create a vector of countries to group as "other countries"
countries_to_group <- c("Switzerland", "France", "United Kingdom", "Germany", "United States of America", "Belgium", "Spain")

# Reshape data from wide to long format
data_long <- data[data$F82_Total < 30000 & data$F82_01 < 30000,] %>%
  pivot_longer(
    cols = F82_01:F82_07,
    names_to = "Spending_Category",
    values_to = "Amount"
  )

# Calculate the average spending for each country and each category
average_spending <- data_long %>%
  mutate(F05_02_ENG_grouped = if_else(F05_02_ENG %in% countries_to_group, F05_02_ENG, "Other Countries")) %>%
  group_by(F05_02_ENG_grouped, F05_01_ENG) %>%
  summarize(Average_Spending = mean(Amount, na.rm = TRUE)) %>%
  ungroup() %>%
  arrange(desc(Average_Spending))

# Optional: Aggregate to country level without distinguishing by category
average_spending_by_country <- average_spending %>%
  group_by(F05_02_ENG_grouped, F05_01_ENG) %>%
  summarize(Average_Spending = mean(Average_Spending, na.rm = TRUE)) %>%
  arrange(desc(Average_Spending))

# Plot the average spending by country in descending order
ggplot(average_spending_by_country, aes(x = reorder(F05_02_ENG_grouped, -Average_Spending), y = Average_Spending, fill = F05_01_ENG)) +
  geom_bar(stat = "identity") +
  labs(title = "Average Spending by Country", x = "Country", y = "Average Spending") +
  scale_fill_brewer(palette = "Set3", name = "Continent") + # Color based on continent
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        legend.position = "bottom")  # Position the legend at the bottom


```

Once again, looking at the average with a package, it is North American again.
:::

For the plots above, we removed outliers (spending of more than 30'000 CHF) because these observations biased the rest of the sample. We assumed that it was probable that most respondents with spending above 30'000 made an error in the currency, using their local currency to answer questions instead of CHF.

### Distribution of Currency

Now, it is of interest to check which currency was the most used by travelers.

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# Calculate the frequency and percentage of each currency value
currency_data <- data %>%
  count(F80) %>%
  mutate(Percentage = n / sum(n) * 100)

# Create a bar chart
ggplot(currency_data, aes(x = reorder(F80, desc(Percentage)), y = Percentage, fill = F80)) +
  geom_bar(stat = "identity", fill = "skyblue") + 
  geom_text(aes(label = paste0(round(Percentage, 1), "%")), vjust = -0.5, size = 3, color = "black") + 
  labs(title = "Distribution of Currency", x = "Currency", y = "Percentage (%)") +
  ylim(0, 100) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  scale_fill_discrete(name = "Currency")
```

We observed that most visitors spend in Swiss Francs or Euros. Other currencies are less used. As mentioned above, we assumed that some people used their currencies when putting their spendings, which created outliers in our results.

## Travel partners of visitors

```{r, echo=FALSE, output=FALSE, warning=FALSE, error=FALSE}
data <- read.csv(here("data","TMS_dataset_Vaud_20240314_FINAL.csv"), sep = ",")

explanations <- read.csv(here("data","explanations.csv"))

which(colnames(data) == "F31_01")
which(colnames(data) == "F32")

df <- data[, 18:33]

# Keep english columns only
seq(2, 17, 2)
df <- df[, seq(2, 17, 2)]

# Set responses to binary values
for (i in 1:ncol(df)) {
  df[, i] <- ifelse(df[, i] == "Applies", 1, ifelse(df[, i] == "Not applicable", 0, NA))
}

# We add a column to separate couples from families. Here people only traveled with their partner.

df$couples <- ifelse(df$F31_02_ENG == 1 & df$F31_03_ENG == 0 & df$F31_04_ENG == 0 & df$F31_05_ENG == 0, 1, 0)

# Sums of responses for frequency plot
df_sums <- list()

for (col in names(df)) {
  df_sums[[col]] <- sum(df[[col]])
}

# ggplot of frequency of responses
df_sums_df <- data.frame(Column = names(df_sums), Sum = unlist(df_sums))

#Change column names in df_sums_df
df_sums_df$Column <- c("Alone", "Partner", "Friends", "Children", "Other family", "Unknown people (group)", "Dog", "Other pet(s)", "Only with partner")
colnames(df_sums_df)[colnames(df_sums_df) == "Traveled with"] <- "Column"

# Sort by descending sum
df_sums_df$Column <- factor(df_sums_df$Column, levels = df_sums_df$Column[order(-df_sums_df$Sum)])

#Plot frequency of "traveled with" groups
#ggplot(df_sums_df, aes(x = Column, y = Sum)) +
#  geom_bar(stat = "identity", fill = "skyblue") +
#  labs(title = "Frequency of responses", x = "Traveled with", y = "Sum")

# make the plot in percentages

df_sums_df$Percentage <- (df_sums_df$Sum)/nrow(df)*100
```

These are the responses to the question "Who did you travel with?". All the bars in this plot are non-mutually exclusive responses, meaning respondents could select multiple options, except for the bar "Only with partner", in which case the respondent only selected "traveled with partner".

```{r, echo = FALSE, message = FALSE, warning = FALSE}
ggplot(df_sums_df, aes(x = Column, y = Percentage)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  geom_text(aes(label = paste0(round(Percentage, 1), "%")), vjust = -0.5, size = 3, color = "black") +
  labs(title = "Frequency of responses", x = "Traveled with", y = "Percentage") +
  ylim(0, 100)
```

We notice that more than 2/3 of overall visitors came to Vaud with their partner (68.7%). Of these, 43% came only with their partner, without friends, children or other family. Almost 1/3 of visitors came with their children. Only a small fraction of people visited Vaud alone (14.6%), and a minority of people took their pet(s) with them (6.5%).

# Methodology

After receiving the raw data, we cleaned and translated it to create a main CSV data file. Following this, we wrote the EDA (Exploratory Data Analysis) section to display single variables/responses as graphs and plots, to get a better idea of the scale and type of responses in the survey. We also present the missing observations (NAs) in this section.

The main results of the analysis is divided into two parts. The first part, Analysis, presents correlations between multiple variables/responses in the forms of plots and graphs. The second part, Maps, gives a visual representation of different responses with respect to Vaud's districts, which helps us categorize tourists geographically.

Finally, we will present our final takeaways and recommendations based on our findings.
